---
title: "Developint Editing tool"
output: html_document
runtime: shiny 
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup}
library(igraph)
library(visNetwork)
library(shinyjs)
devtools::load_all()
```

## Executive Summary

Yo, a little background here. Developing Schema to modify `visNetwork`
Change is really not the most intuitive way.

### When to prepend Namespace?

The First challenge is with `namespace`. There are a few situation you
need to reconsider namespace in server: - in `visNetworkProxy` this the
id needs to be ns() - in `visEvent` (so this function basically expose a
few more clickable html component available to shiny via javascript
`Shiny.onInputChange` or `Shiny.setInputValue`. The input id created by
this will be made available as it is... . But because in any shiny
server module context, any input, output will get automatically
**prefixed** id, server written will access wrong Id. (do so use a
`sprintf`).

With current `visNetworkVersion` anyway... in future this may change.
They should have update this anyway

Following situation do not need namespace, even it input is passed as
string argument: - update input (default shiny) - using anything you set
up with `shinyjs`

### Triva about the `<visNetworkId>_graphChange` input id

Input id of manipulation option. If you accidentally change namespace of
the visNetworkId you will have to change the following too. It is a
painfully process. If you don't realise this will take you a while to
debug.

This happens to me when a restyle visNetworkOutput id from `plot` to
`visNetworkId`

### Split Code

The reason for restyling is so I can use `mod_visNetworkRead()` server.

## Lab Area

### Create Object

```{r}
g <- igraph::make_graph(~ A-+B:C,
                        B-+D:E, C-+F:G
)

# g <- igraph::make_tree(30, 3)
g_length <- length(V(g))
e_length <- length(E(g))
V(g)$name <- seq(g_length) |> as.character() |> paste0(".name")
V(g)$attr_1 <- sample(seq(10), g_length, replace = T)
V(g)$attr_2 <- sample(LETTERS, g_length, replace = T)
E(g)$attr1 <- sample(LETTERS, e_length, replace = T)
E(g)$attr2 <- sample(seq(10), e_length, replace = T)
# E(g)$name <- seq(e_length) |> as.character()
E(g)$id <- seq(e_length) |> as.character() |> paste0(".id")
```

### Run Shiny Module Preview

```{r}
mod_visNetworkWrite_ui("id")
# function(input, output, session) {
mod_visNetworkWrite_server("id", reactive(g))
# }
```

### View Origin

```{r}
E(g)$title <- pasteEdgeDetails(g)
V(g)$title <- pasteNodeDetails(g)
visIgraph(g)
```

Okay modify graph is a bit tricky. There are a few concept you need to
know.

## Figure out a schematic of update network

### Reactive Value

First is shiny `reactiveValues`. This is the only method that let you
write change an object (it's sister `reactiveVal` is pretty much
useless).

Object accessed via `reactiveValues$x` will be automatically reactive.
Assign is allowed so I guess this is some sort of active field.

### Index Edge

The second concept is igraph operation, igraph vertex indexing.

```{r}
g <- igraph::make_graph(~ A-+B:C,
                        B-+D:E, C-+F:G
)
# turns out you can subset vertex by just using 
E(g)[.inc("A")] # incident vertex of A
E(g)[.from("A")] # from vertex of A
E(g)[.to("B")] # to vertex of B
E(g)["F" %--% "C"] # edge between F and C
E(g)["A" %->% "B"]

new_g <- g + edge(1, 4)
new_g <- g + edge("A", "G")
visIgraph(new_g)
```

Igraph have "interesting" way of decideing which ones are id which ones
are not.

### `_graphChange$cme == "editEdge"`

This one is really tricky, because you need to find ways to save edge
attributes data and assign it to another way.

Yet our shiny app track edge id by a randomly assigned uid, **unless you
specify yourself**.

Now what happen if we use tidygraph? Nope! nothing changes!

if you have both id and name in your igraph? For edge, you can only use
id. Apparently it have a preference for col name `id`

What about uid? Nope! only recognize `id`

```{r eval = FALSE}

# g - edge("2.id", by = "id") # this won't run
g - edge("2.name", by = "2") # this will
g - edge(2)
g - edge("2")


delete_edges(g, )

get.edge.ids(g, c(1, 2))
E(g)$id
```

Igraph preper edge name over an attribute named id.. But in visNetwork
any attribute named `id` or `name` will be interpreated as edge

## Use Binding Reactive Values

```{r eval=FALSE}
library(shiny)

ui <- fluidPage(
  verbatimTextOutput("text"),
  sliderInput("init", "set original Value (a)", min = 1, max = 5,value = 2),
  sliderInput("set", "stage value (b)", min = 1, max = 5,value = 2),
  actionButton("commit", "commit change")
)

server <- function(input, output, session) {
  x <- reactive(1)
  g <- reactiveValues(a = NULL,
                      b = NULL)
  output$text <- renderPrint({
    print(sprintf("a is: %i", g$a))
    print(sprintf("b is : %i", g$b))
    print(glue::glue(
      "the difference between `x` (a reactive expression) and 
       `g$a` (a reactive value) is `x` is type of {mode(x)}, 
      `g$a` type of {mode(g$a)}"
    ))
  })
  observe({
    g$a <- input$init
    g$b <- input$init
    print("initial Assignment")
  })
  
  observe({
    g$b <- input$set
  })
  observeEvent(input$commit, {
    g$a <- g$b 
    updateSliderInput(inputId = 'init', value = g$a)
    updateSliderInput(inputId = 'set', value = g$b)
  })
}
shinyApp(ui, server)
```

## Igraph id versus VisNetwork id

For some awkward reasons igraph vertex is identified by attribute
"name", vertex is by "id". What is more confusing is in tidygraph id
name is "names"

| Package    | Node Identifier | Edge Identifier |
|------------|-----------------|-----------------|
| igraph     | name            | id              |
| visNetwork | id              | id, from, to;   |
| tidygarph  | NULL            | from, to;       |

Okay let's test this theory

```{r}
# EXP1: NULL EXPERIMENT ------------------------------------------------------------------
ig = igraph::make_star(6) # this graph object have null attributes
ig |> vertex_attr_names() # this return nothing
ig |> toVisNetworkData() |> purrr::pluck("nodes") |> names() # you get "id" "label" out of nowhere

ig |> edge_attr_names() # this also return nothing 
ig |> toVisNetworkData() |> purrr::pluck("edges") |> names() # you get "from" "to" of a sudden 
# EXP2: NAME IS AN ATTRIBUTE IN IGRAPH
V(ig)$name = seq(length(V(ig))) |> as.character()
ig |> vertex_attr_names()
ig |> toVisNetworkData() |> purrr::pluck("nodes") |> names() # "name" attribute is swapped to "id"

# EXP3: NAMES (plural) IS AN ATTRIBUTE
ig = igraph::make_star(6)
V(ig)$names = seq(length(V(ig))) |> as.character()
ig |> vertex_attr_names()
ig |> toVisNetworkData() |> purrr::pluck("nodes") |> names()  # "names" is kept

# EXP4: ID IS AN ATTRIBUTE
ig = igraph::make_star(6)
V(ig)$id = sample(LETTERS, length(V(ig)))
ig |> vertex_attr_names()
ig |> toVisNetworkData() |> purrr::pluck("nodes") |> names()
ig |> vertex_attr("id", 1) # specifically use id as output
ig |> toVisNetworkData() |> purrr::pluck("nodes", 1, 1) # "id" is completely overwritten replace with integers
```

Here is your take away:

-   avoid using "id" when you transfer data between igraph and
    VisNetwork\
