---
title: How to style a visNetwork Object?
---


Method provided by them do not work
```{.r}
nodes <- data.frame(id = 1:3, label = paste("Node", 1:3))
edges <- data.frame(from = c(1,2), to = c(1,3), label = paste("Edge", 1:2))
network <- visNetwork(nodes, edges)

library(shiny)

ui <- fluidPage(
  sidebarLayout(
    sidebarPanel = visNetworkEditorUI("id"),
    mainPanel = visNetworkOutput("plot")
  )
)

server <- function(input, output, session) {
  output$plot = renderVisNetwork({
    network
  })
  callModule(visNetworkEditorServer, "id", 
             object = reactive(visNetworkProxy("plot"))
             )
}
```


```{r}
visNetworkOptions = list(
  shape = "box",
  color = "color",
  node = "node"
)
```



```{r}
library(shiny)

g = igraph::make_tree(23, 3)
V(g)$name = sample(LETTERS, length(V(g))) |> paste(sample(LETTERS, length(V(g))))
ui <- fluidPage(
  visNetworkOutput("visNetwork"),
)

server <- function(input, output, session) {
  output$visNetwork = renderVisNetwork({
    visIgraph(g) |> 
      visSetOptions(options = 
                      list(nodes = 
                             list(
                               shape = "box", 
                                color= list(
                                  background = "black",
                                  border = "black"
                                  ),
                                font= list(
                                  color = "white"
                                  ),
                                title = p("helo"),
                                chosen = list(
                                  node = "function(values, id, selected, hovering) {
                                          values.property = chosenValue;
                                          }"
                                )
                                ),
                   edges = list(arrows = "to"),
                   layout = list(
                     hierarchical = T
                   )
                              ))
  })
}

shinyApp(ui, server)
```

Okay, with this I can easily implement something like gloabl option. 

I need to create a reactive list of options at the begaingin. 
Two list actually, 

One four all available options scoped, 
the other something else, 

Need flatten the first option and lappy it into UI component.
Parse it into something like `opt.visnetwork.nodes.font.color`. Then I need some sort
of dynamic scheme


The one needs a little transfrom are: 

  - list as hierarchical layout
  - layout as circle implementing igraph layout
  
Those two should be implemented 


They other thing is how do I set option conditionally? As set option locally?

```{r}

```

