---
title: "Developint Editing tool"
output: html_document
runtime: shiny 
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup}
library(igraph)
library(visNetwork)
library(shinyjs)
devtools::load_all()
```

## Executive Summary

Yo, a little background here. Developing Schema to modify visNetwork
Change is really not the most intuitive way.

### When to prepend Namespace?

The First challenge is with `namespace`. There are a few situation you
need to reconsider namespace in server: - in `visNetworkProxy` this the
id needs to be ns() - in `visEvent` (so this function basically expose a
few more clickable html component available to shiny via javascript
`Shiny.onInputChange` or `Shiny.setInputValue`. The input id created by
this will be made available as it is... . But because in any shiny
server module context, any input, output will get automatically
**prefixed** id, server written will access wrong Id. (do so use a
`sprintf`).

With current `visNetworkVersion` anyway... in future this may change.
They should have update this anyway

Following situation do not need namespace, even it input is passed as
string argument: - update input (default shiny) - using anything you set
up with `shinyjs`

### Triva about the `<visNetworkId>_graphChange` input id

Input id of manipulation option. If you accidentally change namespace of the visNetworkId you will have to change the following too. It is a painfully process. If you don't realise this will take you a while to debug.


## Lab Area

### Create Object

```{r}
g <- igraph::make_graph(~ A-+B:C,
                        B-+D:E, C-+F:G
)

# g <- igraph::make_tree(30, 3)
g_length <- length(V(g))
e_length <- length(E(g))
V(g)$name <- seq(g_length) |> as.character() |> paste0(".name")
V(g)$attr_1 <- sample(seq(10), g_length, replace = T)
V(g)$attr_2 <- sample(LETTERS, g_length, replace = T)
E(g)$attr1 <- sample(LETTERS, e_length, replace = T)
E(g)$attr2 <- sample(seq(10), e_length, replace = T)
# E(g)$name <- seq(e_length) |> as.character()
E(g)$id <- seq(e_length) |> as.character() |> paste0(".id")
```

### Run Shiny Module Preview

```{r}
mod_visNetworkWrite_ui("id")
# function(input, output, session) {
mod_visNetworkWrite_server("id", reactive(g))
# }
```

### View Origin

```{r}
E(g)$title <- pasteEdgeDetails(g)
V(g)$title <- pasteNodeDetails(g)
visIgraph(g)
```

Okay modify graph is a bit tricky. There are a few concept you need to
know.


## Figure out a schematic of update network

### Reactive Value

First is shiny `reactiveValues`. This is the only method that let you
write change an object (it's sister `reactiveVal` is pretty much
useless).

Object accessed via `reactiveValues$x` will be automatically reactive.
Assign is allowed so I guess this is some sort of active field.

### Index Edge

The second concept is igraph operation, igraph vertex indexing.

```{r}
g <- igraph::make_graph(~ A-+B:C,
                        B-+D:E, C-+F:G
)
# turns out you can subset vertex by just using 
E(g)[.inc("A")] # incident vertex of A
E(g)[.from("A")] # from vertex of A
E(g)[.to("B")] # to vertex of B
E(g)["F" %--% "C"] # edge between F and C
E(g)["A" %->% "B"]

new_g <- g + edge(1, 4)
new_g <- g + edge("A", "G")
visIgraph(new_g)
```

Igraph have "interesting" way of decideing which ones are id which ones
are not.

### `_graphChange$cme == "editEdge"`

This one is really tricky, because you need to find ways to save edge
attributes data and assign it to another way.

Yet our shiny app track edge id by a randomly assigned uid, **unless you
specify yourself**.

Now what happen if we use tidygraph? Nope! nothing changes!

if you have both id and name in your igraph? For edge, you can only use
id. Apparently it have a preference for col name `id`

What about uid? Nope! only recognize `id`

```{r eval = FALSE}

# g - edge("2.id", by = "id") # this won't run
g - edge("2.name", by = "2") # this will
g - edge(2)
g - edge("2")


delete_edges(g, )

get.edge.ids(g, c(1, 2))
E(g)$id
```

Igraph preper edge name over an attribute named id.. But in visIgraph
any attribute named `id` or `name` will be interpreated as edge

## Use Binding Reactive Values

```{r eval=FALSE}
library(shiny)

ui <- fluidPage(
  verbatimTextOutput("text"),
  sliderInput("init", "set Initial Value", min = 1, max = 5,value = 2),
  sliderInput("set", "set value b to", min = 1, max = 5,value = 2),
  actionButton("commit", "commit change")
)

server <- function(input, output, session) {
  g <- reactiveValues(a = NULL,
                      b = NULL)
  output$text <- renderPrint({
    print(sprintf("a is: %i", g$a))
    print(sprintf("b is : %i", g$b))
  })
  observe({
    g$a <- input$init
    g$b <- input$init
    print("initial Assignment")
  })
  
  observe({
    g$b <- input$set
  })
  observeEvent(input$commit, {
    g$a <- g$b 
  })
}
shinyApp(ui, server)
```
